The globular cluster system of the Auriga simulations

### 2019-08-16 AurigaGCS.tex
Updated Figure 1 for #1

% Abstract of the paper
\begin{abstract}
We investigate whether the galaxy formation model used for the Auriga simulations
can produce a realistic globular cluster (GC) population at redshift zero. We
compare properties of the simulated star particles in the Auriga haloes with
catalogues of observations of the Milky Way (MW) and Andromeda (M31) globular
cluster populations available in the literature. We find that the Auriga 
simulations do produce sufficient mass at radii and metallicities that are 
typical for the MW globular cluster system (GCS), although we observe a varying 
mass-excess for different $R_{\text{GC}}$-[Fe/H] bins of simulated GC candidates
relative to the observed mass in the MW and M31 GC systems. This implies different 
values for the combined product of the bound cluster formation efficiency and 
the globular cluster disruption rate. Furthermore we test whether any of the 
Auriga galaxies has a metallicity and radial distribution that is consistent with 
the MW or M31 GCS. For any one of the Auriga haloes we reject the null hypothesis
that the observed and simulated metallicities of GCs (GC candidates) are drawn
from the same distribution at $\geq98.32$~\% confidence level, for the GCS of 
the Milky Way as well as that of the Andromeda galaxy. The same holds true for 
the distribution of galactocentric radius. Overall, the Auriga simulations produce 
old star particles with higher metallicities than the MW and M31 GCS and at 
larger radii. The formation efficiency would have to linearly decrease with 
increasing metallicity for the Auriga GC candidates to be consistent with the 
MW GCS, if cluster disruption is equally efficient regardless of metallicity.
In addition, the number of GCs relative to field stars would have to be smaller
for higher metallicity star particles at large radii than for those with lower 
metallicity at smaller radii, assuming GC disruption is more efficient in the
inner regions of the Galaxy.

@@

\subsection{Milky Way}
\label{sec:milkyway}
\citet[][2010 edition; hereafter H96e10]{1996AJ....112.1487H} provides a
catalogue\footnote{See \url{https://www.physics.mcmaster.ca/Fac_Harris/mwgc.dat}}
of the Milky Way globular cluster system that contains properties of
157 GCs. The authors initially estimated the size of the MW GCS to be 180~$\pm$~10,
thus, their catalogue to be ${\sim}$85\% complete. However, an additional 59 GCs
are claimed to have been discovered by various authors. The total number of GCs
in the MW might add up to 216 with recent estimates now anticipating an additional 
thirty GCs yet to be discovered \citep[e.g.][and references therein]{2018ApJ...863L..38R}.
We still use data from the Harris catalogue, but caution that it may (only) be
53-72\% complete. Specifically, the relevant data fields that we use from H96e10
are the metallicity [Fe/H], the Galactic distance components $X$, $Y$, and $Z$ (in
kpc)\footnote{In a Sun-centered coordinate system: $X$ points toward Galactic
center, $Y$ in direction of Galactic rotation, and $Z$ toward the North Galactic
Pole. We calculate the galactocentric radius $R_{\text{GC}}=\sqrt{(X-R_\odot)^2
+ Y^2 + Z^2}$, assuming the solar radius $R_\odot=8$~kpc.}, and absolute
magnitude in the V-band $M_V$. We use the latter to calculate mass-estimates by
assuming $M_{V,\odot}=4.83$ and a mass to light ratio $M/L_V = 1.7$~M/L$_{\odot}$,
the mean for MW clusters \citep{2005ApJS..161..304M}. We supplement the catalogue
with age-estimates from isochrone fits to stars near the main-sequence turnoff 
in 55 GCs \citep[][hereafter V13]{2013ApJ...775..134V}.

@@

\subsection{Radial distribution}
\label{sec:Rgc}
The bottom panel of Figure~\ref{fig:MW-M31-age-Rgc} shows the radial distribution
of the MW and M31 GCS. Both quantities are readily available in H96e10 (assuming
$R_{\odot}=8.0$~kpc), but the galactocentric radius of GCs in M31 is not available
in CR16. Therefore we follow \citet[][Sec.~4.1]{2019arXiv190111229W} to calculate
the projected radius $R_{\text{proj}}$ from the observed positions, adopting M31's
central position from the NASA Extragalactic 
Database\footnote{\url{https://ned.ipac.caltech.edu/}} $(\alpha_0, \, \delta_0) =
(0^{\text{h}}42^{\text{m}}44.35^{\text{s}}, \, +41^{\circ}16'08.63")$
and distance $D_{\text{M31}} = 780$~kpc \citep{2005MNRAS.356..979M,2012ApJ...758...11C}.
We calculate $R_{\text{GC}}$ as `average deprojected distance`
$R_{\text{GC}} = R_{\text{proj}} \times (4/\pi)$.

The solid lines show the distributions using all available data (because the
sky coordinates are known for each GC), while the subset for which age-estimates
are available is indicated using dotted lines. The latter shows a narrower range
of radii than the full data set: it appears that age-estimates are neither
available for the innermost ($<1$~kpc) GCs, nor for those beyond roughly twenty
kpc (the halo GCs). We compare both distributions of the full data set (solid 
lines) and find that the Milky Way has more GCs in the range $1-4$~kpc than M31
(when accounting for the larger number of total GCs in M31). Interestingly, both
distributions show a similar trend for $R_{\text{GC}} > 4$~kpc and host a 
subpopulation of halo GCs. However, both radial distributions are not 
statistically consistent due to substantial differences at intermediate radii.

\begin{figure}
    \includegraphics[width=\columnwidth]{{MW_M31_Age_Histogram-trim}.png}
    \includegraphics[width=\columnwidth]{{MW_M31_Rgc_Histogram-trim}.png}
    \caption{
        \emph{Top}: Age distribution of 55 GCs in the MW
        \citep[data from][]{2013ApJ...775..134V} and 88 GCs
        in M31 \citep[data from][]{2016ApJ...824...42C}.
        \emph{Bottom:} Distribution of galactocentric radius in the MW and M31.
        The dotted lines show the subset of data that also have age measurements
        (i.e. the same sample as used in the top panel).
        \label{fig:MW-M31-age-Rgc}
    }
\end{figure}

\subsection{Total GC mass in metallicity-radial space} \label{sec:observations_FeHRgc}
We show the two-dimensional mass-weighted metallicity-radial distribution of the
MW (M31) GCS in the top (bottom) panel of Figure~\ref{fig:observations_FeHRgc}. 
The observations indicate that
no GCs with high metallicities are to be expected at large radii (the three bins
in the upper right corner, both for MW and M31), and relatively few GCs at large
radii in general ($R_{\text{GC}} > 30$~kpc; right column: $11$ GCs or 7.3\% in
the MW and $17$ or 4.6\% in M31). Moreover, the M31 hosts more metal-rich 
([Fe/H]$ > -1$) GCs in each radial bin in comparison to the MW GCSs than what
would be expected when accounting for the fact that Andromeda hosts a larger GC 
system than the MW. Finally, given that both marginalized (i.e. the metallicity 
and radial) distributions are not statistically consistent, we find that the 
two-dimensional distributions are also not consistent. More generally, the GC
systems of the Milky Way and that of Andromeda both differ significantly. We 
compare these observations to the Auriga simulations later on in 
Sec.~\ref{sec:results_FeHRgc}.

\begin{figure}
    \includegraphics[width=\columnwidth]
        {{MW_RgcFeH_HistogramMassWeighted_Harris1996ed2010data}.png}
    \includegraphics[width=\columnwidth]
        {{M31_RgcFeH_HistogramMassWeighted_CaldwellRomanowsky2016data}.png}
    \caption{
        \emph{Top}: Mass-weighted $R_{\text{GC}}$-[Fe/H] distribution of
        151 GCs in the MW \citep[data from][2010 ed.]{1996AJ....112.1487H}, which
        is 98.6 (92.2) \% of the total mass (clusters) of the MW GCS in the Harris
        catalog. \emph{Bottom}: Same for M31, showing 366 GCs and 88.4 (83.9) \%
        of the total mass (clusters) in CR16 \citep[data from][]{2016ApJ...824...42C}.
        Note that the range of the colourmap differs in both figures.
        \label{fig:observations_FeHRgc}
    }
\end{figure}

@@

\begin{figure}
    \includegraphics[width=\columnwidth]{{LogRgc_mu_sigma-trim}.png}
    \caption{
        Mean and standard deviation of the logarithm of radial distribution 
        of star particles in each of the thirty Auriga L4 haloes compared to
        the MW (M31) GCS shown in purple (magenta).
        \label{fig:Rgc_mu_sigma}
    }
\end{figure}
We repeat the analysis of the previous subsection for the distribution of
galactocentric radius instead of metallicity. We look for general trends present
in all Auriga L4 galaxies. Figure~\ref{fig:Rgc_mu_sigma} shows the mean and 
standard deviation of $\log_{10}(R_{\text{GC}})$ of star particles in all Auriga
L4 simulations. The purple (magenta) cross again shows the mean of the MW (M31)
GCs (which are to be compared to the green crosses), but solid (open) dot now
shows our calculation of the mean value of the metal-rich (metal-poor) population 
as no literature values were available. We split the radii up into the 
metal-rich/metal-poor groups by taking a metallicity cut at [Fe/H]~=~-1 as is 
done in the literature.

We notice that the old {\it in~situ} populations are more centrally 
distributed, whereas the old accreted subsets have a larger radial extent. This 
is not surprising because the classification of {\it in~situ} requires star particles 
to have formed within the virial radius, thus they could naturally be expected 
to end up at small galactocentric radii. Accreted star particles, on the other 
hand, have formed in another (sub)halo beyond the virial radius, thus, would 
first have to migrate inwards in order to populate the innermost radii. Moreover,
we find that the simulations have a wider dispersion in $\log(R_{\text{GC}}$ than
the MW GCS, while the dispersion of M31 seems to lie witin the range of dispersions
found in the Auriga galaxies. Furthermore, the mean of the MW GCS lies roughly 
within the range of values produced by the Auriga simulations, whereas the mean 
of M31 is somewhat larger and slightly closer to typical mean values of the 
accreted GC candidates in the Auriga simulations. The larger radial extent 
of the M31 GCS is generally believed to hint at a more accretion-dominated origin 
of the GCS, and may reflect a richer accretion history of the galaxy in comparison 
to the Milky Way.

@@

We investigate whether the Auriga simulations still produce sufficient mass when
the GC candidates are two-dimensionally binned in [Fe/H] and $R_\text{GC}$. First
we sum the total simulated mass in each bin (for an individual Auriga simulation),
then we calculate the median over all thirty Auriga L4 haloes (in each bin, see
Figure~\ref{fig:Au-FeHRgc} which can be compared to
Figure~\ref{fig:observations_FeHRgc}). Finally, we divide these value by the total
mass in the MW (M31) GCS to obtain the median mass excess produced by the star
formation model implemented in the Auriga simulations. See the top (bottom) panel
of Figure~\ref{fig:Au-FeHRgc-ratio} for mass excess with respect to the MW (M31) GCS.

\begin{figure}
    \includegraphics[width=0.49\textwidth]
        {{Au4-median_RgcFeH_HistogramMassWeighted_iold-trim}.png}
    \caption{
        Mass-weighted [Fe/H]-$R_{\text{GC}}$ distribution of all thirty Auriga
        L4 haloes. Here we consider only the GC candidates (age $>$~10~Gyr) stars
        in and color-code by the \textbf{median} (values also shown in each bin).
        The numbers in parenthesis show how many star particles fall within the
        bin. Note that the range of the colourmap again differs (for improved
        contrast within the plot).
        \label{fig:Au-FeHRgc}
    }
\end{figure}

@@

\subsection{Radial distribution}
\label{sec:discussion_Rgc}
The M31 GCS has a factor 2-3 more GCs at large radii compared to the MW GCS,
which may indicate that M31 has a richer merger history than the MW 
\citep{2016ApJ...824...42C}. In the Auriga simulations we find that the GC 
candidates at radii larger than ${\sim}20$~kpc are indeed dominated by accreted
star particles. However, we select star particles that are bound to the main 
halo and main subhalo, which means that we include particles up to the virial 
radius $R_{200}$. The Auriga simulations have no problem populating the stellar 
halo up to the virial radius, even with our additional age cut. On the other hand, 
the MW and M31 have fewer GCs at large radii. We expect tidal disruption to be
less efficient at larger radii, thus, the formation efficiencies of the accreted 
GC candidates would have to be lower. Our classification as GC candidates could, 
for example, be improved by selecting a number of globular clusters based on the 
$M_{vir}-N_{\text{GC}}$ correlation found by \citet{2019arXiv190100900B}, and 
taking a virial mass below which none of the star particles is treated as GC candidate.

>>>>

% Abstract of the paper
\begin{abstract}
We investigate whether the galaxy formation model used for the Auriga simulations
can produce a realistic globular cluster (GC) population at redshift zero. We
compare properties of the simulated star particles in the Auriga haloes with
catalogues of observations of the Milky Way (MW) and Andromeda (M31) globular
cluster populations available in the literature. We find that the Auriga 
simulations do produce sufficient mass at radii and metallicities that are 
typical for the MW globular cluster system (GCS), although we observe a varying 
mass-excess for different galactocentric radius-metallicity 
($R_{\text{gal}}$-[Fe/H]) bins of simulated GC candidates
relative to the observed mass in the MW and M31 GC systems. This implies different 
values for the combined product of the bound cluster formation efficiency and 
the globular cluster disruption rate. Furthermore we test whether any of the 
Auriga galaxies has a metallicity and radial distribution that is consistent with 
the MW or M31 GCS. For any one of the Auriga haloes we reject the null hypothesis
that the observed and simulated metallicities of GCs (GC candidates) are drawn
from the same distribution at $\geq98.32$~\% confidence level, for the GCS of 
the Milky Way as well as that of the Andromeda galaxy. The same holds true for 
the distribution of $R_{\text{gal}}$ . Overall, the Auriga simulations produce 
old star particles with higher metallicities than the MW and M31 GCS and at 
larger radii. The formation efficiency would have to linearly decrease with 
increasing metallicity for the Auriga GC candidates to be consistent with the 
MW GCS, if cluster disruption is equally efficient regardless of metallicity.
In addition, the number of GCs relative to field stars would have to be smaller
for higher metallicity star particles at large radii than for those with lower 
metallicity at smaller radii, assuming GC disruption is more efficient in the
inner regions of the Galaxy.

@@

\subsection{Milky Way}
\label{sec:milkyway}
\citet[][2010 edition; hereafter H96e10]{1996AJ....112.1487H} provides a
catalogue\footnote{See \url{https://www.physics.mcmaster.ca/Fac_Harris/mwgc.dat}}
of the Milky Way globular cluster system that contains properties of
157 GCs. The authors initially estimated the size of the MW GCS to be 180~$\pm$~10,
thus, their catalogue to be ${\sim}$85\% complete. However, an additional 59 GCs
are claimed to have been discovered by various authors. The total number of GCs
in the MW might add up to 216 with recent estimates now anticipating an additional 
thirty GCs yet to be discovered \citep[e.g.][and references therein]{2018ApJ...863L..38R}.
We still use data from the Harris catalogue, but caution that it may (only) be
53-72\% complete. Specifically, the relevant data fields that we use from H96e10
are the metallicity [Fe/H], the Galactic distance components $X$, $Y$, and $Z$ (in
kpc)\footnote{In a Sun-centered coordinate system: $X$ points toward Galactic
center, $Y$ in direction of Galactic rotation, and $Z$ toward the North Galactic
Pole. We calculate the galactocentric radius $R_{\text{gal}}=\sqrt{(X-R_\odot)^2
+ Y^2 + Z^2}$, assuming the solar radius $R_\odot=8$~kpc.}, and absolute
magnitude in the V-band $M_V$. We use the latter to calculate mass-estimates by
assuming $M_{V,\odot}=4.83$ and a mass to light ratio $M/L_V = 1.7$~M/L$_{\odot}$,
the mean for MW clusters \citep{2005ApJS..161..304M}. We supplement the catalogue
with age-estimates from isochrone fits to stars near the main-sequence turnoff 
in 55 GCs \citep[][hereafter V13]{2013ApJ...775..134V}.

@@

\subsection{Radial distribution}
\label{sec:Rgc}
The bottom panel of Figure~\ref{fig:MW-M31-age-Rgc} shows the radial distribution
of the MW and M31 GCS. Both quantities are readily available in H96e10 (assuming
$R_{\odot}=8.0$~kpc), but the galactocentric radius of GCs in M31 is not available
in CR16. Therefore we follow \citet[][Sec.~4.1]{2019arXiv190111229W} to calculate
the projected radius $R_{\text{proj}}$ from the observed positions, adopting M31's
central position from the NASA Extragalactic 
Database\footnote{\url{https://ned.ipac.caltech.edu/}} $(\alpha_0, \, \delta_0) =
(0^{\text{h}}42^{\text{m}}44.35^{\text{s}}, \, +41^{\circ}16'08.63")$
and distance $D_{\text{M31}} = 780$~kpc \citep{2005MNRAS.356..979M,2012ApJ...758...11C}.
We calculate $R_{\text{gal}}$ as `average deprojected distance`
$R_{\text{gal}} = R_{\text{proj}} \times (4/\pi)$.

The solid lines show the distributions using all available data (because the
sky coordinates are known for each GC), while the subset for which age-estimates
are available is indicated using dotted lines. The latter shows a narrower range
of radii than the full data set: it appears that age-estimates are neither
available for the innermost ($<1$~kpc) GCs, nor for those beyond roughly twenty
kpc (the halo GCs). We compare both distributions of the full data set (solid 
lines) and find that the Milky Way has more GCs in the range $1-4$~kpc than M31
(when accounting for the larger number of total GCs in M31). Interestingly, both
distributions show a similar trend for $R_{\text{gal}} > 4$~kpc and host a 
subpopulation of halo GCs. However, both radial distributions are not 
statistically consistent due to substantial differences at intermediate radii.

\begin{figure}
    \includegraphics[width=\columnwidth]{{MW_M31_Age_Histogram-trim}.png}
    \includegraphics[width=\columnwidth]{{MW_M31_Rgc_Histogram-trim}.png}
    \caption{
        \emph{Top}: Age distribution of 55 GCs in the MW
        \citep[data from][]{2013ApJ...775..134V} and 88 GCs
        in M31 \citep[data from][]{2016ApJ...824...42C}.
        \emph{Bottom:} Distribution of galactocentric radius in the MW and M31.
        The dotted lines show the subset of data that also have age measurements
        (i.e. the same sample as in the top panel).
        \label{fig:MW-M31-age-Rgc}
    }
\end{figure}

\subsection{Total GC mass in metallicity-radial space} \label{sec:observations_FeHRgc}
We show the two-dimensional mass-weighted metallicity-radial distribution of the
MW (M31) GCS in the top (bottom) panel of Figure~\ref{fig:observations_FeHRgc}. 
The observations indicate that
no GCs with high metallicities are to be expected at large radii (the three bins
in the upper right corner, both for MW and M31), and relatively few GCs at large
radii in general ($R_{\text{gal}} > 30$~kpc; right column: $11$ GCs or 7.3\% in
the MW and $17$ or 4.6\% in M31). Moreover, the M31 hosts more metal-rich 
([Fe/H]$ > -1$) GCs in each radial bin in comparison to the MW GCSs than what
would be expected when accounting for the fact that Andromeda hosts a larger GC 
system than the MW. Finally, given that both marginalized (i.e. the metallicity 
and radial) distributions are not statistically consistent, we find that the 
two-dimensional distributions are also not consistent. More generally, the GC
systems of the Milky Way and that of Andromeda both differ significantly. We 
compare these observations to the Auriga simulations later on in 
Sec.~\ref{sec:results_FeHRgc}.

\begin{figure}
    \includegraphics[width=\columnwidth]
        {{MW_RgcFeH_HistogramMassWeighted_Harris1996ed2010data}.png}
    \includegraphics[width=\columnwidth]
        {{M31_RgcFeH_HistogramMassWeighted_CaldwellRomanowsky2016data}.png}
    \caption{
        \emph{Top}: Mass-weighted $R_{\text{gal}}$-[Fe/H] distribution of
        151 GCs in the MW \citep[data from][2010 ed.]{1996AJ....112.1487H},
        color-coded by the \textbf{median} (values also shown in each bin). The 
        numbers in parenthesis show how many star particles fall within the bin.
        \emph{Bottom}: Same for M31, showing the 366 GCs in CR16 
        \citep[data from][]{2016ApJ...824...42C}. Note that the range of the 
        colourmap differs in both figures.
        \label{fig:observations_FeHRgc}
    }
\end{figure}

@@

\begin{figure}
    \includegraphics[width=\columnwidth]{{LogRgc_mu_sigma-trim}.png}
    \caption{
        Mean and standard deviation of the logarithm of radial distribution 
        of star particles in each of the thirty Auriga L4 haloes compared to
        the MW (M31) GCS shown in purple (magenta).
        \label{fig:Rgc_mu_sigma}
    }
\end{figure}
We repeat the analysis of the previous subsection for the distribution of
galactocentric radius instead of metallicity. We look for general trends present
in all Auriga L4 galaxies. Figure~\ref{fig:Rgc_mu_sigma} shows the mean and 
standard deviation of $\log_{10}(R_{\text{gal}})$ of star particles in all Auriga
L4 simulations. The purple (magenta) cross again shows the mean of the MW (M31)
GCs (which are to be compared to the green crosses), but solid (open) dot now
shows our calculation of the mean value of the metal-rich (metal-poor) population 
as no literature values were available. We split the radii up into the 
metal-rich/metal-poor groups by taking a metallicity cut at [Fe/H]~=~-1 as is 
done in the literature.

We notice that the old {\it in~situ} populations are more centrally 
distributed, whereas the old accreted subsets have a larger radial extent. This 
is not surprising because the classification of {\it in~situ} requires star particles 
to have formed within the virial radius, thus they could naturally be expected 
to end up at small galactocentric radii. Accreted star particles, on the other 
hand, have formed in another (sub)halo beyond the virial radius, thus, would 
first have to migrate inwards in order to populate the innermost radii. Moreover,
we find that the simulations have a wider dispersion in $\log(R_{\text{gal}})$ than
the MW GCS, while the dispersion of M31 seems to lie witin the range of dispersions
found in the Auriga galaxies. Furthermore, the mean of the MW GCS lies roughly 
within the range of values produced by the Auriga simulations, whereas the mean 
of M31 is somewhat larger and slightly closer to typical mean values of the 
accreted GC candidates in the Auriga simulations. The larger radial extent 
of the M31 GCS is generally believed to hint at a more accretion-dominated origin 
of the GCS, and may reflect a richer accretion history of the galaxy in comparison 
to the Milky Way.

@@

We investigate whether the Auriga simulations still produce sufficient mass when
the GC candidates are two-dimensionally binned in [Fe/H] and $R_\text{gal}$. First
we sum the total simulated mass in each bin (for an individual Auriga simulation),
then we calculate the median over all thirty Auriga L4 haloes (in each bin, see
Figure~\ref{fig:Au-FeHRgc} which can be compared to
Figure~\ref{fig:observations_FeHRgc}). Finally, we divide these value by the total
mass in the MW (M31) GCS to obtain the median mass excess produced by the star
formation model implemented in the Auriga simulations. See the top (bottom) panel
of Figure~\ref{fig:Au-FeHRgc-ratio} for mass excess with respect to the MW (M31) GCS.

\begin{figure}
    \includegraphics[width=0.49\textwidth]
        {{Au4-median_RgcFeH_HistogramMassWeighted_iold-trim}.png}
    \caption{
        Mass-weighted [Fe/H]-$R_{\text{gal}}$ distribution of all thirty Auriga
        L4 haloes. Here we consider only the GC candidates (age $>$~10~Gyr) stars
        in and color-code by the \textbf{median} (values also shown in each bin).
        The numbers in parenthesis show how many star particles fall within the
        bin. Note that the range of the colourmap again differs (for improved
        contrast within the plot).
        \label{fig:Au-FeHRgc}
    }
\end{figure}

@@

\subsection{Radial distribution}
\label{sec:discussion_Rgc}
The M31 GCS has a factor 2-3 more GCs at large radii compared to the MW GCS,
which may indicate that M31 has a richer merger history than the MW 
\citep{2016ApJ...824...42C}. In the Auriga simulations we find that the GC 
candidates at radii larger than ${\sim}20$~kpc are indeed dominated by accreted
star particles. However, we select star particles that are bound to the main 
halo and main subhalo, which means that we include particles up to the virial 
radius $R_{200}$. The Auriga simulations have no problem populating the stellar 
halo up to the virial radius, even with our additional age cut. On the other hand, 
the MW and M31 have fewer GCs at large radii. We expect tidal disruption to be
less efficient at larger radii, thus, the formation efficiencies of the accreted 
GC candidates would have to be lower. Our classification as GC candidates could, 
for example, be improved by selecting a number of globular clusters based on the 
$M_{vir}-N_{\text{gal}}$ correlation found by \citet{2019arXiv190100900B}, and 
taking a virial mass below which none of the star particles is treated as GC candidate.
